Learning and comparing functional connectomes between populations

### 2012-09-04 paper.tex
More iteration

AAL, Harvard-oxford

@@

@@

Correlation, shrinkage of correlation, partial correlation, sparse iCov.

@@

@@

@@

@@

\cite{mcintosh1994}

@@

Setting the cursor between bio-physical models

>>>>

AAL \cite{tzourio-mazoyer2002a}, Harvard-oxford, sulci-based atlas.
Personal bias against the AAL.

@@

FMRI signals contributing to functional connectivity
have been found to lie in frequencies below 0.1 Hz \cite{cordes2000}
XXX: but cite recent work that shows that there is info at higher
frequency.

@@

Correlation, shrinkage of correlation \cite{ledoit2004,varoquaux2012},

Remark: difference between covariance and correlation matrix.

partial correlation, sparse iCov. \cite{smith2011,varoquaux2010b}.

Give intuition on partial correlation/inverse covariance.

Variety
of estimation strategies for sparse iCov, that have an impact on the
resulting network \cite{varoquaux2012}\footnote{Better estimation
algorithm is recent Honorio paper.}. Discuss setting the regularization
parameter.

@@

Boils down to a standard linear model => t-tests and co.
Stress that to have Gaussian-distributed correlations, a Fisher Z
transform is required.

Multiple comparison problem is quite an issue (scales a $p^2$) =>
permutation and max-T approach XXX: cite Ge
"resampling-based multiple testing for microarray data analysis", and
Nichols multiple comparison paper.

@@

Show that correlations co-fluctuation with images.

Ad-hoc model: network-based statistics \cite{zalesky2010}

Discuss the 'residual' strategy?
\cite{varoquaux2010b}

@@

Small world networks, transport properties, resilient...

Warning note that correlation matrices have long-tailed degree
distribution by definition (cite recent Bullmore paper showing that).

@@

\cite{mcintosh1994}
\cite{marrelec2007}
\cite{marrelec2009}

@@

Setting the cursor between complex models based on a bio-physical
description, and simple phenomenological models such as correlation
matrices.
